Cross-Validation SIPHER7 Equivalent Income

### 2024-01-19 docsrc/documentation/notebooks/housing.Rmd

---
title: "Housing"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Housing Quality

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

## References

>>>>

---
title: "Housing"
output: html_document
bibliography: 
  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

## Housing Quality

@@

```{r housing_barchart, echo=FALSE}
discrete_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", 'next_housing_quality')
```

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds", "next_housing_quality") 
clm_output("data/transitions/housing_quality/clm/housing_quality_2018_2019.rds")
```

### References

### 2024-01-19 minos/outcomes/equivalent_income_out.Rmd

---
title: "Equivalent Income Outcome Visualisation"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

@@

```{r}
# set output path to SIPHER 7 experiment out
out.path <- here::here('output', 'SIPHER7/')
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
allchild.dat <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
pov.dat <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
wage.dat <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
energy.dat <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)
```

## Remove 2020 Data Point

```{r}
base.dat <- filter(base.dat, time > 2020)
allchild.dat <- filter(allchild.dat, time > 2020)
pov.dat <- filter(pov.dat, time > 2020)
wage.dat <- filter(wage.dat, time > 2020)
energy.dat <- filter(energy.dat, time > 2020)
```

@@

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

@@

ggplot(data = base.subset, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()
```

@@

```{r}
equivalent_income_comparison_fullpop <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base %>%
    select(pidp, time, equivalent_income, alive, weight) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  int.subset <- int %>%
    select(pidp, time, equivalent_income, alive, weight) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

@@

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')
```

@@

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
base.subset$scenario <- 'Baseline'

allchild.subset <- allchild.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
allchild.subset$scenario <- 'AllChild'

pov.subset <- pov.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
pov.subset$scenario <- 'PovertyChild'

wage.subset <- wage.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
wage.subset$scenario <- 'LivingWage'

energy.subset <- energy.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
energy.subset$scenario <- 'EnergyDownlift'

@@

```{r}
equivalent_income_comparison_treated <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    rename(baseline = equivalent_income)
  int.sub <- int %>%
    select(pidp, time, equivalent_income, income_boosted, alive, weight) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    set_names(c('pidp', 'time', int.name, 'income_boosted', 'weight'))

@@

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))

@@

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')
```

@@

allchild.boosted <- allchild.merged %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  filter(income_boosted == 'True' | time == 2020) %>%
  mutate(adjusted_EI = allchild - boost_amount) %>%
  select(-allchild, -income_boosted, -boost_amount) %>%
  group_by(time) %>%
  summarise(baseline = mean(baseline),
            allchild_adj = mean(adjusted_EI)) %>%
  pivot_longer(cols = baseline:allchild_adj,
               names_to = 'scenario',
               values_to = 'equivalent_income')
```

```{r}
ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()
```

@@

# DETAILED ANALYSIS

## Living Wage

For this, we're going to look at the difference in equivalent income and try to explain it by looking at the pathway variables. What we want to see is that as income is uplifted, the various pathways show a positive shift and that in part explains the difference in equivalent income.

First visualise both income and equivalent income on one graph.

### Income and Equivalent Income

```{r}
base.inc <- base.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')

int.inc <- wage.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Living_Wage')

combined <- rbind(base.inc, int.inc)
combined <- combined %>%
  pivot_longer(cols=hh_income:equivalent_income,
               names_to = 'income_type',
               values_to = 'value')

ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
  geom_line() +
  facet_wrap( ~ income_type, nrow=2, scales='free')
```

### CHANGE IN INCOME / EQUIVALENT INCOME

```{r}
base.inc <- base.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')

int.inc <- energy.dat %>%
  select(pidp, time, hh_income, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
            equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'EnergyCrisis')

combined <- rbind(base.inc, int.inc)
combined <- combined %>%
  pivot_longer(cols=hh_income:equivalent_income,
               names_to = 'income_type',
               values_to = 'value')

ggplot(combined, aes(x = time, y = value, group = source, color = source)) +
  geom_line() +
  facet_wrap( ~ income_type, nrow=2, scales='free')
```

How about on the same plot to make it more clear?

```{r}
income_equivinc_change <- function(base.dat, int.dat) {
  base.inc <- base.dat %>%
    select(pidp, time, hh_income, equivalent_income, weight) %>%
    group_by(time) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  int.inc <- int.dat %>%
    select(pidp, time, hh_income, equivalent_income, weight) %>%
    group_by(time) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

  combined <- merge(base.inc, int.inc, by = c('time'))

  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income

  combined <- combined %>%
    pivot_longer(cols = diff_income:diff_equiv_income,
                 names_prefix = 'diff_',
                 names_to = 'variable',
                 values_to = 'diff')

  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype = 'dashed')
}

income_equivinc_change(base.dat, energy.dat)
income_equivinc_change(base.dat, wage.dat)
```

## Energy Crisis

```{r}
S7_ordinal_pathway_vis <- function(base.dat, int.dat, int.name, var) {
  base.hous <- base.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

  inc.hous <- int.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = int.name)

  combined <- rbind(base.hous, inc.hous)
  combined[[var]] <- as.factor(combined[[var]])

  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
    geom_line() +
    geom_point()

  print(p1)

  base.hous2 <- base.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(Baseline = prop)

  int.hous2 <- int.dat %>%
    select(pidp, time, all_of(var)) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(int = prop)

  combined2 <- merge(base.hous2, int.hous2, by = c('time', var))

  combined2[[var]] <- as.factor(combined2[[var]])

  combined2$diff <- combined2$int - combined2$Baseline

  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]])) +
    geom_line() +
    geom_point()

  print(p2)
}
```

### Housing Quality

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_housing_quality')
```

### Neighbourhood Safety

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_neighbourhood_safety')
```

### Mental Wellbeing

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_mental_health')
```

### Physical Health

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_physical_health')
```

### Loneliness

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'loneliness')
```

### Labour State

```{r}
S7_ordinal_pathway_vis(base.dat, energy.dat, 'EnergyCrisis', 'S7_labour_state')
```

```{r}
boosted.pidps <- energy.dat %>%
  filter(income_boosted == 'True') %>%
  select(pidp)

base.hous <- base.dat %>%
  select(pidp, time, S7_housing_quality) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time, S7_housing_quality) %>%
  count() %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prop = (n / total) * 100) %>%
  select(-n, -total) %>%
  rename(Baseline = prop)

int.hous <- energy.dat %>%
  select(pidp, time, S7_housing_quality, income_boosted) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time, S7_housing_quality) %>%
  count() %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prop = (n / total) * 100) %>%
  select(-n, -total) %>%
  rename(EnergyCrisis = prop)

combined <- merge(base.hous, int.hous, by = c('time', 'S7_housing_quality'))

combined$diff <- combined$EnergyCrisis - combined$Baseline

ggplot(combined, aes(x = time, y = diff, group = S7_housing_quality, color = S7_housing_quality)) +
  geom_line() +
  geom_point()
```

```{r}
## just look at means in case the means are causing some problems
base.dat.2 <- base.dat
base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'No to all'] <- 1
base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to some'] <- 2
base.dat.2$S7_housing_quality2[base.dat.2$S7_housing_quality == 'Yes to all'] <- 3
wage.dat.2 <- energy.dat
wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'No to all'] <- 1
wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to some'] <- 2
wage.dat.2$S7_housing_quality2[wage.dat.2$S7_housing_quality == 'Yes to all'] <- 3

base.hous.mean <- base.dat.2 %>%
  select(pidp, time, S7_housing_quality2, weight) %>%
  group_by(time) %>%
  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'Baseline')
wage.hous.mean <- wage.dat.2 %>%
  select(pidp, time, S7_housing_quality2, weight) %>%
  group_by(time) %>%
  summarise(mean_housing = weighted.mean(S7_housing_quality2, w = weight, na.rm = TRUE)) %>%
  mutate(source = 'EnergyCrisis')

combined <- rbind(base.hous.mean, wage.hous.mean)

ggplot(combined, aes(x = time, y = mean_housing, group = source, color = source)) +
  geom_line() +
  geom_point()
```

```{r}

# df <- combine_and_pivot_long(base.dat, 'Baseline', wage.dat, 'LivingWage', c('S7_housing_quality', 'income_boosted'))
# 
# outcomes.prep <- function(base.dat, int.dat, int.name, var) {
#   boosted.pidps <- int.dat %>%
#     filter(income_boosted == 'True') %>%
#     select(pidp, time)
#   
#   df1 <- base.dat %>%
#     select(pidp, time, all_of(var), weight) %>%
#     
# }
# 
# 
# 
# 
# combine_and_pivot_long <- function(df1, df1.name, df2, df2.name, var) {
#   # get only the columns we want a rename
#   df1 <- df1 %>%
#     select('pidp', 'time', all_of(var)) %>%
#     set_names(c('pidp', 'time', df1.name))
#   df2 <- df2 %>%
#     select('pidp', 'time', all_of(var)) %>%
#     set_names(c('pidp', 'time', df2.name))
#   # merge on pidp and time
#   merged <- merge(df1, df2, by = c('pidp', 'time'), all=TRUE)
#   pivoted <- pivot_longer(data = merged,
#                           cols = df1.name:df2.name,
#                           names_to = 'scenario',
#                           values_to = var)
#   return(pivoted)
# }

>>>>

---
title: "Equivalent Income Outcome Visualisation"
output: html_notebook
---

@@

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/validation/utils.r')
```

@@

```{r}
# set output path to SIPHER 7 experiment out
out.path <- 'Minos/output/SIPHER7/'
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_output(out.path, 'baseline')
allchild.dat <- read_output(out.path, 'hhIncomeChildUplift')
pov.dat <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
wage.dat <- read_output(out.path, 'livingWageIntervention')
energy.dat <- read_output(out.path, 'energyDownlift')
```

@@

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))

@@

ggplot(data = base.subset, aes(x = time, y = equivalent_income)) +
  geom_line()
```

@@

```{r}
equivalent_income_comparison_fullpop <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = mean(equivalent_income))
  int.subset <- int %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    group_by(time) %>%
    summarise(equivalent_income = mean(equivalent_income))

@@

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
```

@@

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
base.subset$scenario <- 'Baseline'

allchild.subset <- allchild.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
allchild.subset$scenario <- 'AllChild'

pov.subset <- pov.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
pov.subset$scenario <- 'PovertyChild'

wage.subset <- wage.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
wage.subset$scenario <- 'LivingWage'

energy.subset <- energy.dat %>%
  select(pidp, time, equivalent_income, alive) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income))
energy.subset$scenario <- 'EnergyDownlift'

@@

```{r}
equivalent_income_comparison_treated <- function(base, int, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base.dat %>%
    select(pidp, time, equivalent_income, alive) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    rename(baseline = equivalent_income)
  int.sub <- int %>%
    select(pidp, time, equivalent_income, income_boosted, alive) %>%
    filter(alive != 'dead') %>%
    select(-alive) %>%
    set_names(c('pidp', 'time', int.name, 'income_boosted'))

@@

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2021) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario) %>%
    summarise(equivalent_income = mean(equivalent_income))

@@

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/MINOS/Minos/plots/Equivalent_Income/')
```

@@

allchild.boosted <- allchild.merged %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  filter(income_boosted == 'True' | time == 2021) %>%
  mutate(adjusted_EI = allchild - boost_amount) %>%
  select(-allchild, -income_boosted, -boost_amount) %>%
  group_by(time) %>%
  summarise(baseline = mean(baseline),
            allchild_adj = mean(adjusted_EI)) %>%
  pivot_longer(cols = baseline:allchild_adj,
               names_to = 'scenario',
               values_to = 'equivalent_income')

ggplot(data = allchild.boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_line()

@@

### 2024-01-19 minos/validation/cross_validation_S7.Rmd

```{r}
inc.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2014)
print(inc.14)
```
```{r}
inc.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2016)
print(inc.16)
```
```{r}
inc.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2018)
print(inc.18)
```
```{r}
inc.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2021)
print(inc.20)
rm(inc.14, inc.16, inc.18, inc.20)
```

@@

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'equivalent_income')
multi_year_boxplots(raw, cv, 'equivalent_income')
snapshot_OP_plots(raw, cv, 'equivalent_income', target.years = c(2014, 2017, 2020))
q_q_comparison(raw, cv, 'equivalent_income')
```
```{r}
ei.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2014)
print(ei.14)
```
```{r}
ei.17 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2017)
print(ei.17)
```
```{r}
ei.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2020)
print(ei.20)
rm(ei.14, ei.17, ei.20)
```

>>>>

```{r}
inc.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2015)
print(inc.14)
```
```{r}
inc.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2017)
print(inc.16)
```
```{r}
inc.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2019)
print(inc.18)
```
```{r}
inc.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'hh_income', 
                                 target.year = 2021)
print(inc.20)
rm(inc.14, inc.16, inc.18, inc.20)
```

@@

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'equivalent_income')
multi_year_boxplots(raw, cv, 'equivalent_income')
snapshot_OP_plots(raw, cv, 'equivalent_income', target.years = c(2017, 2020))
q_q_comparison(raw, cv, 'equivalent_income')
```
```{r}
# ei.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
#                                  predicted = cv, 
#                                  var = 'equivalent_income', 
#                                  target.year = 2014)
#print(ei.14)
```
```{r}
ei.17 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2017)
print(ei.17)
```
```{r}
ei.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2020)
print(ei.20)
rm(ei.14, ei.17, ei.20)
```
